Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/figs/eval-ocr-ner.tex
Update OCR results with kraken
MAJ Part 3

  \node [above left=0cm of A, font=\it] {OCR Prediction};
  \node [above left=0cm of B, font=\it] {GOLD};

@@

  \draw[-latex] (C.south) -- ++(0,-1) node[midway,right,font=\small] {OCR Q.A.} node[below] {CER = 24\%};
  \draw[-latex] (D.south) -- ++(0,-1) node[midway,right,font=\small] {NER reference.};
  \draw[-latex] (C.south east) |- (E2) node[pos=0.75,below, font=\it] {NER Prediction};
  \draw[-latex] (E2.south) -- ++(0,-1) node[midway,right,font=\small] {NER Q.A.}
  node[below] {Precision = 33\%, Recall = 25\%, F-score = 0.4};
\end{tikzpicture}

>>>>

  \node [above left=0cm of A, font=\it] {OCR-\emph{prediction}};
  \node [above left=0cm of B, font=\it] {GOLD};

@@

  \draw[-latex] (C.south) -- ++(0,-1) node[midway,right,font=\small] {OCR Q.A.} node[below] {CER = 24\%};
  \draw[-latex] (D.south) -- ++(0,-1) node[midway,right,font=\small] {NER-\emph{target}};
  \draw[-latex] (C.south east) |- (E2) node[pos=0.75,below, font=\it] {NER-\emph{prediction}};
  \draw[-latex] (E2.south) -- ++(0,-1) node[midway,right,font=\small] {NER Q.A.}
  node[below] {Precision = 66\%, Recall = 50\%, F-score = 0.4};
\end{tikzpicture}
